Draft

### 2017-09-08 Thesis/Draft.tex
Add descriptions to Appendix

The thesis at hand joins the ranks of a large literature concerned with
the general problem of sequential sampling. One is familiar with the
idea of ``batch sampling'', where the entire sample is gathered first
and analyzed only after the last sample has become available. However,
as noted in Chernoff (1958), many situations arise in which one would
like to gather feedback from samples as they are drawn so as to
influence the choice of the next sample. The two fundamental
characteristics of the latter sampling process are that it is sequential
and adaptive. Since observations are drawn in sequence, one has a chance
to observe the observations drawn so far in order to adapt the decision
of what sample one would like to observe next.

This makes sequential sampling especially relevant in situations where
there is a inherent cost to drawing an observation. The classical
example that of clinical trials in which a researcher tests two drugs on
patients to observe which one performs better. Not only is it difficult
to gather patients, but also one would like to adapt the sampling such
that as soon as possible more patients receive the better drug so that
more patients are cured. As noted in Cappé et al. (2013), this example
dates back to Thompson (1933, 1935). Such problems are known as
multi-armed bandit problems in which the sampling is adapted so as to
minimize the cumulative regret: In the case of the drug tests, one would
like to sample the two drugs in a way to find the best drug as soon as
possible and then to test this drug more and more often and more often
than the worse drug. This would lead to cumulatively more healthy
patients then when both drugs are tested uniformly and thus minimize the
regret from treating a patient with an ineffective drug.

Instead of drugs, can consider two or more unknown distributions (which
we call arms in the multi-armed bandit problem). These distributions
have different means, and one can draw samples sequentially from the
distributions in order to estimate their means. One would like to play
the distribution with the highest mean to minimize the cumulative regret
measure. How can we organize the sampling in order to achieve this goal?

While Gittins (1979) presents an Bayesian-optimal solution, the
Upper-Confidence Bound algorithms pioneered by Agrawal (1995) and Auer,
Cesa-Bianchi and Fischer (2002) lead to a blooming literature on
multi-armed bandit problems that has been picked up to solve modern
problems in website and advertising optimization, where advertisers try
to allocate their advertising optimally so as to reduce regret from
showing poorly converting advertisements. Several algorithms as the
KL-UCB algorithm based on Kullback-Leibler divergence upper confidence
intervals (Cappé et al., 2013) or the Bayes-UCB algorithm (Kaufmann et
al., 2012) have followed and been shown to be optimal as they reach the
lower bound introduced in Lai and Robbins (1985) and Burnetas and
Katehakis (1996).

These algorithms have in common that they compute after any sample an
index for each of the unknown distributions. This index is based solely
on the past (observed) data, and then used to pick the distribution from
which the next observation should be drawn. Using these indexes, the
algorithms can sequentially sample and adapt the future strategies to
observations as they are gathered.

Other algorithms based on indices can be used on related problems.
Instead of minimizing cumulative regret, it might be more interesting to
find the best arm, that is, the distribution with the largest mean, with
as few samples as possible and with confidence as large as possible.
This is particularly useful when there is not necessarily a cost from
initially picking a lower mean, but when drawing any sample is costly,
and one needs to explore the distributions as efficiently as possible.
The need for strategies other than uniform sampling arises: Do not
continue to sample distributions that we are confident about. As such,
the best arm identification problem is very similar to the problem faced
in Bayesian Optimization: Training large neural networks is costly in
terms of time and computation, and so the parameter space needs to be
explored with as few samples as possible. (Zhang et al., 2017; Brochu et
al., 2010).

The problem of best arm identification is very related to statistical
hypothesis testing as noted by Chernoff (1958) since in the end, one has
to make a decision about how the means of distributions relate to each
other. The main difference of course being that the sampling procedure
becomes integrated into the evaluation of the distributions. Given the
focus on exploration, the problem is usually described with a loss
function different from cumulative regret. Audibert et al. (2010)
introduce a soft measure called \emph{simple regret} based on which they
describe UCB policies. Other authors investigate hard, binary measures
that are equal to 1 when the best arm has not been identified (Russo,
2016; Garivier and Kaufmann, 2016). These binary measures correspond to
the probability of the identified arm being the best, and thus
inherently related to hypothesis testing. The problem of best arm
identification can readily be extended to the so called Top-\(m\)
problem of identifying the best \(m\) of \(K\) arms (Kaufmann and
Kalyanakrishnan, 2013; Kaufmann et al. 2016).

In this thesis, we consider the thresholding bandit problem. Instead of
identifying the best \(m\) out of \(K\) arms, one aims to find all out
of \(K\) distributions that have a mean larger than a threshold fixed
upfront. In the form described in Locatelli et al. (2016), algorithms in
the thresholding bandit problem are evaluated against a binary loss
function penalizing whenever an arm has not been classified correctly as
being above the threshold and thus focus on exploration similar to
algorithms employed for best arm identification. Indeed, Locatelli et
al. (2016) show how their thresholding algorithm can be used for best
arm identification when the mean of the best arm is known upfront.

In the following, we first present the thresholding bandit problem in
detail. To then extend upon the algorithm proposed by Locatelli et al.
(2016), we first explore how the Kullback-Leibler divergence has been
employed in the best arm identification literature by Garivier and
Kaufmann (2016) and Kaufmann et al. (2016). We shortly describe two
variance based algorithms for the thresholding bandit problem introduced
in Mukherjee et al. (2017) and Zhang et al. (2017), before introducing
the new Simple Likelihood Ratio algorithm. We end with experiments to
examine the performance of different algorithms.

@@

To introduce the thresholding bandit problem, consider a game in which
the learner is tasked to find those slot machines within a row of \(K\)
slot machines in a casino that give a mean payoff larger than a fixed
threshold \(\tau\), for example \(\tau = 0\). The learner cannot pull
all slot machines at the same time. Instead, he acquires samples
sequentially from one slot machine at a time to learn about their payoff
structure. The learner has a budget of \(T\) slot machine pulls. After
\(t-1\) samples, the learner has observed \(T_i(t-1)\) samples from slot
machine \(i\). The payoffs \(X_{i,1}, ..., X_{i,T_i(t-1)}\) are drawn
from the payoff distribution \(\nu_i\) underlying the slot machine
\(i\). At time \(t\), the learner considers the payoffs he observed so
far in order to choose the next slot machine he would like to pull. His
decision is lead by the goal to classify the slot machines with
distribution \(\nu_i\) and mean payoff
\(\mu_i = \mathbb{E}_{X \sim \nu_i}[X]\) after \(T\) samples as being
above or below the threshold with error probability as small as
possible.

The thresholding bandit problem can thus be framed in the wide
literature on sequential sampling strategies. While its name is
reminiscient of the multi-armed bandit setting, the thresholding bandit
problem is more akin to best arm identification and Top-\(m\)
identification problems due to its focus on exploration: While the
classical multi-armed bandit problems are concerned with cumulative
regret which increases \emph{during} sampling, best arm identification
and thresholding bandits collect loss only once \emph{after} the
sampling procedure (compare Garivier and Kaufmann, 2016; Kaufmann et
al., 2016; Kaufmann and Kalyanakrishnan, 2013). Furthermore, as there
arises an implicit threshold between the means of the \(m\)-th best arm
and the \(m+1\)-th best arm (Kaufmann et al., 2016; Kaufmann and
Kalyanakrishnan, 2013), algorithms for the Top-\(m\) identification
problem classify arms at least implicitly as being above or below a
threshold. The two settings are thus very related.

@@

Consider a setting with a set of \(\mathbb{A}=\{1, ..., K\}\) unknown
probability distributions \(\nu_i, i \in \mathbb{A}\). To stick with the
idea of multi-armed bandits, we call those distributions arms, and
observations from those arms rewards (Bubeck and Cesa-Bianchi, 2012).
The learner is interested in learning about the structure of the arms;
in particular, he would like to estimate the means \(\mu_1, ..., \mu_K\)
by sequentially drawing observations \(X_{i,1}, X_{i,2}, ...\) from each
arm. However, at time \(t\) the learner cannot observe a reward from
every distribution but must select a single arm \(I_t\) from which he
would like to observe the reward \(X_{I_t,t}\). An adaptive sampling
strategy makes the decision of which arm to pull usually by computing an
index \(B_i(t)\) for each arm. If \(T_i(t)\) is the number of samples
observed until time \(t\) for arm \(i\), then \(B_i(t)\) is a function
of the past rewards \(X_{i,1}, ..., X_{i,T_i(t)}\) observed for arm
\(i\), and w.l.o.g. \(I_t = \arg \min_{i = 1,...K} B_i(t)\). The set of
indices can be called strategy (Kaufmann et al., 2012) which makes it
clear that the strategy is adapted as more observations are collected.
Strategies of this kind are also called index policies.

What index proves to be useful is determined by the loss function with
which the decisions of the algorithm are evaluated. While many problems
are concerned with finding the arm with the largest mean \(\mu_i\), in
which algorithms collect loss either cumulatively (Auer and
Cesa-Bianchi, 2012) or once at the end of the sampling (Kaufmann et al.,
2016), the thresholding bandit problem considers a slightly different
loss function. Consider a fixed threshold value \(\tau \in \mathbb{R}\)
and an epsilon interval \(\tau \pm \epsilon\) around the threshold for
\(\epsilon \geq 0\). As mentioned in the introduction, the learner is
tasked with classifying arms as having a mean \(\mu_i\) larger or
smaller than \(\tau\). To describe which arms are above the threshold,
we introduce the following set notation (compare Locatelli et al.,
2016): Let \(\mathcal{S}_{\tau}\) be the set of distributions in
\(mathbb{A}\) with mean larger than the threshold:
\(\mathcal{S}_{\tau} := \{i \in \mathbb{A}, \mu_i \geq \tau\}\).
Consequently, the complement is given by the arms with mean below the
threshold,
\(\mathcal{S}^C_{\tau} := \{i \in \mathbb{A}, \mu_i < \tau\}\).

The thresholding problem for the learner is now to use a budget of
overall \(T\) samples (or rounds) to explore the different arms. After
this exploration phase, the learner has to return a set of arms that he
believes to have a mean above the threshold. The problem can thus be
described by the threshold \(\tau\) and a precision \(\epsilon\). When
evaluating the classification of the learner, arms with mean inside of
the epsilon interval will not be considered. The learner only has to
distinguish the means from the threshold correctly up to the precision
\(\epsilon\). Thus, the algorithm is not evaluated against
\(\mathcal{S}_{\tau}\) and \(\mathcal{S}^C_{\tau}\), but needs to
distinguish \(\mathcal{S}_{\tau+\epsilon}\) from
\(\mathcal{S}^C_{\tau-\epsilon}\). As in Locatelli et al. (2016),
whenever we say that ``an arm is over the threshold'', we mean that the
mean of the arm is over the threshold.

@@

\[
\mathcal{L}(T) = \mathbbm{1}{(\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \lor (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset)}
\]

In order to perform well, a learner has to identify all arms that are
over the threshold as such, and to not claim arms as being over the
threshold if they actually are below the threshold. Due to the precision
\(\epsilon\), the loss is not influenced by arms which are too close to
the threshold \(\tau\), that is, arms inside of the
\(\tau \pm \epsilon\) interval. If either \(\hat{\mathcal{S}}_{\tau}\)
contains an arm below \((\tau - \epsilon)\), or
\(\hat{\mathcal{S}}^C_{\tau}\) contains an arm above
\((\tau + \epsilon)\), a loss of \(1\) is accrued. Else, all arms
outside the epsilon interval are classified correctly and the loss is
equal to \(0\). In the case of \(\epsilon = 0\), all arms need to be
classified correctly to not endure any loss.

@@

which corresponds to the probability of making a wrong classification.
Both the probability of not identifying an arm that is actually over the
threshold, as well as the probability of accepting an arm as over the
threshold when it is not are evaluated. The oracle strategy would
evaluate all arms correctly with an error probability of \(0\)
(Locatelli et al., 2016).

At this point, we have introduced the general thresholding bandit
problem setting which we will use throughout the thesis. The setting
might be extended by different assumptions to make certain algorithms or
bounds feasible. For that reason, Locatelli et al. (2016) assume that
the distributions \(\nu_i, i \in \mathbb{A}\) are \(R\)-sub-Gaussian.
Under this assumption, the authors are able to prove a lower bound on
the largest probability of error of the best algorithm in the setting we
have just introduced, as well as an upper bound on the performance of
their APT algorithm we will introduce in the following chapter. As in
their paper, we define \(R\)-sub-Gaussian and assume it in the
description of their algorithm and bounds:

@@

As noted by Locatelli et al. (2016), this ensures that the mean
\(\mu_i\) of the distributions \(\nu_i\) considered in our problem are
finite. \(R\)-sub-Gaussian distributions furthermore offer concentration
inequalities for the concentration of the empirical mean to the true
mean, which makes it possible to deduce the bounds presented by the
authors and repeated below. The family of \(R\)-sub-Gaussian
distributions encompasses Gaussian distributions of variance \(R^2\) for
\(R \in \mathbb{R}\), as well as all bounded distributions, with the
important case of Bernoulli distributions.

@@

Just like the general index policies mentioned in \autoref{sec:Setup},
we see that the APT algorithm adapts its strategy using an index
\(B_i(t+1)\) for each arm that is based entirely on the observations
observed until time \(t\). Given the arm with the smallest index is
pulled at round \(t+1\), we observe that arms that are estimated to be
further away from the threshold \(\tau\) as measured by the absolute
distance to their empirical mean \(\hat{\mu}_i\), \(\hat{\Delta}_i(t)\),
are pulled less often. Intuitively, it is easier to classify arms as
below or above \(\tau\) when their mean is far away from the threshold.
In contrast to the uniform sampling strategy, APT will gather more
evidence for arms which appear to be inherently more difficult to
classify. Likewise, APT tends to pull arms less often which it already
pulled considerably often as measured by \(T_i(t)\). If arm \(i\) has
been pulled more often than arm \(j\), then we should in general be more
confident in its estimated mean and the corresponding distance to the
threshold. If we are confident in \(i\), then it is better to explore
other arms by drawing an observation from arm \(j\). By adapting its
sampling strategy in this way during the sequential sampling process,
the APT algorithm minimizes the probability of error
\(\mathbb{E}[\mathcal{L}(T)]\) after \(T\) samples have been observed.

The previous paragraph describes how arms close to the threshold are
intuitively more difficult to classify. In the index employed by the APT
algorithm, the distance between an arm and the threshold is measured by
the absolute distance \(\hat{\Delta}_i(t)\) between the (estimated) mean
of the arm and the threshold \(\tau\) (and the epsilon interval). Given
that one compares \(B_i^{APT}\) with \(B_j^{APT}\), one could just as
well measure the distance by the squared distance,
\(\hat{\Delta}_i(t)^2\). When the APT algorithm realizes that an arm has
a mean close to the threshold, then this arm requires more attention
than an arm far away from the threshold; the confidence in the empirical
mean has to be larger. Or the empirical mean has to be better
concentrated around the true mean. Otherwise it is easier to make a
mistake on this arm. To gain this confidence, the arm requires more
samples, and thus a larger share of the overall \(T\) samples available.
With this intuition, it makes sense to measure the complexity of a
thresholding problem: If we knew upfront how complex a given set of arms
is, we knew whether we can expect a small or large probability of error
given our budget \(T\). Also, for example in the best arm identification
problem, there exist algorithms which take the complexity of a problem
as input. Based on the complexity they then adapt their sampling
strategy. See for example the UCB-E algorithm in Audibert et al. (2010)
for the best arm identification problem, or the KL-LUCB-E algorithm in
Kaufmann and Kalyanakrishnan (2013) as extension to the Top-\(m\)
problem.

While the APT algorithm does not require the complexity to be known
upfront (which would be problematic), it is necessary to define the
complexity to deduce the upper bound on its probability of error.
Similar to the distance measure used in the algorithm's index, we define
the gap \(\Delta_i^{\tau,\epsilon}\) between arm \(i\) and the threshold
\(\tau \pm \epsilon\) as

@@

Note that the complexity of the problem increases in the number of arms
\(K\) and decreases in the gap \(\Delta_i^{\tau,\epsilon}\).
Consequently, when we require a smaller precision, that is, we increase
\(\epsilon\), the hardness decreases. Furthermore, we see that each arm
contributes its individual complexity,
\(h_i^{\tau,\epsilon} = \frac{1}{(\Delta_i^{\tau,\epsilon})^2}\)
linearly into the problem. Thus, if the complexity \(H\) is a good
measure of the actual problem complexity, and we knew upfront which arm
has which mean, we could allocate the ``optimal'' share of the budget,
\(T \cdot h_i /H\) to arm \(i\). However, since we do not know neither
\(\mu_i\) nor \(H\), the best we can do is to adapt our allocation of
samples more and more towards this optimum as we observe samples.

@@

In this chapter we present the upper bound on the APT algorithm proven
in Locatelli et al. (2016). The upper bound is on the probability of
error that the algorithm has after \(T\) rounds of sampling for a
problem with arms that are assumed to be \(R\)-sub-Gaussian. The bound
depends also on the complexity of the problem, and we show in the proof
that given the index of the APT algorithm as defined in
\autoref{sec:TheAPTAlgorithm}, the complexity \(H\) is an appropriate
measure.

@@

and similar for \(\hat{\Delta}_i\). We can now lower bound the LHS of
the indices as

@@

\begin{equation}
\kappa_C(\nu) = \inf_{A \, \text{PAC}} \limsup_{\delta \to 0} \frac{\mathbb{E}_{\nu}[T{\delta}]}{\log \frac{1}{\delta}}. \label{eq:KappaC}
\end{equation}

@@

\begin{equation}
\kappa_B(\nu) = \inf_{A \, \text{consistent}} \big(\limsup_{t \to \infty} - \frac{1}{t} \log p_t(\nu)\big)^{-1}.
\end{equation}

@@

{\centering \includegraphics[width=0.8\linewidth]{Draft_files/figure-latex/unnamed-chunk-2-1}

@@

>>>>

The thesis at hand joins a large literature concerned with the problem
of sequential sampling. One is familiar with the idea of ``batch
sampling'', where the entire sample is gathered first and analyzed only
after the last sample has become available. However, as noted in
Chernoff (1958), many situations arise in which one would like to gather
feedback from samples as they are drawn, so as to influence the choice
of the next sample. The two fundamental characteristics of the latter
sampling process are that it is sequential and adaptive. Since
observations are drawn in sequence, one has a chance to analyze past
observations in order to adapt the decision of what sample one would
like to observe next.

This makes sequential sampling especially relevant in situations where
there is an inherent cost to obtaining samples. The classical example is
that of clinical trials in which a researcher tests two drugs on
patients to observe which one performs better. Not only is it difficult
to gather enough patients, but one would also like to adapt the sampling
such that as soon as possible more patients receive the better drug and
are cured. As noted in Cappé et al. (2013), this example dates back to
Thompson (1933, 1935). Such problems are known as multi-armed bandit
problems in which the sampling is adapted so as to minimize the
cumulative regret: In the case of the drug tests, one would like to
sample the two drugs in a way to find the best drug as soon as possible
and then to test this drug more and more often and more often than the
worse drug. This would lead to cumulatively more healthy patients than
testing both drugs uniformly; it would minimize the regret from treating
patients with an ineffective drug.

Instead of drugs, one can consider two or more unknown distributions
(which we call arms in the multi-armed bandit problem in analogy with
the one-armed bandit slot machine). These distributions have different
means, and one can draw samples sequentially from the distributions in
order to estimate their means. To minimize the cumulative regret
measure, one would like to play the distribution with the highest mean
as much as possible (\emph{Exploitation}). At the same time, however,
one has to sample all arms at least a little, so as to initially find
the best arm (\emph{Exploration}). Any algorithm thus has to handle a
trade-off between exploration and exploitation to minimize the regret.
How can we organize the sampling in order to achieve this task?

While Gittins (1979) presents an Bayesian-optimal solution to the
cumulative regret problem, the Upper-Confidence Bound (UCB) algorithms
pioneered by Agrawal (1995) and Auer, Cesa-Bianchi and Fischer (2002)
have lead to a blooming literature on multi-armed bandit problems that
has been picked up to solve modern problems in website and advertising
optimization, where advertisers try to allocate their advertising
optimally so as to reduce regret from showing poorly converting
advertisements. Several algorithms like the KL-UCB algorithm based on
Kullback-Leibler divergence upper confidence intervals (Cappé et al.,
2013) or the Bayes-UCB algorithm (Kaufmann et al., 2012) have followed
and been shown to be optimal as they reach the lower bound introduced in
Lai and Robbins (1985) and Burnetas and Katehakis (1996).

These algorithms have in common that they compute after every new sample
an index for each of the unknown distributions. This index is based
solely on the past (observed) data, and then used to pick the
distribution from which the next sample should be drawn. Using these
indexes, algorithms can sample sequentially and adapt their strategies
to observations as they are collected.

Similar algorithms based on indexes can be used on related problems.
Instead of minimizing cumulative regret, it can be of interest to find
the best arm, that is, the distribution with the largest mean -- with as
few samples as possible and with confidence as large as possible. This
is particularly useful when there is not a cost from testing arms with
lower mean, but when drawing any sample is costly. Thus one needs to
explore the distributions as efficiently as possible. Exploitation is
not necessary, and the setting is thus referred to as \emph{Pure
Exploration}. The need for strategies other than uniform sampling
arises: One does not want to continue to sample distributions that one
is confident in. This setting is related to the problem faced in
Bayesian Optimization: Training large neural networks is costly in terms
of time and computation, and so the parameter space needs to be explored
with as few samples as possible. (Zhang et al., 2017; Brochu et al.,
2010). The problem of best arm identification is also very related to
statistical hypothesis testing as noted by Chernoff (1958) since one has
to make a decision about how the means of distributions relate to each
other. The main difference being that the bandit setting includes the
testing procedure in the sampling process.

Given the focus on exploration, the pure exploration problem is usually
described with a loss function different from the one in the cumulative
regret settings. Audibert et al. (2010) introduce a soft measure called
\emph{simple regret} based on which they describe UCB policies. Other
authors investigate binary measures that are equal to 1 when the best
arm has not been identified (Russo, 2016; Garivier and Kaufmann, 2016).
These binary measures correspond to the probability of the identified
arm being the best, and thus inherently related to hypothesis testing.
The problem of best arm identification can readily be extended to the so
called Top-\(m\) problem of identifying the best \(m\) of \(K\) arms
(Kaufmann and Kalyanakrishnan, 2013; Kaufmann et al. 2016).

In this thesis, we consider the thresholding bandit problem. Instead of
identifying the best \(m\) out of \(K\) arms, we aim to find all
distributions out of \(K\) that have a mean at least as large as a
threshold fixed upfront. In the form described in Locatelli et al.
(2016), algorithms in the thresholding bandit problem are evaluated
against a binary loss function penalizing whenever an arm has not been
classified correctly as being above or below the threshold, and thus
focus on exploration similar to algorithms employed for best arm
identification. Indeed, Locatelli et al. (2016) show how their
thresholding algorithm can be used for best arm identification when the
mean of the best arm is known upfront.

In the following, we first present the thresholding bandit problem in
detail in \autoref{chap:ThresholdingBanditProblem}. To then extend upon
the algorithm proposed by Locatelli et al. (2016) and discussed in
\autoref{sec:TheAPTAlgorithm}, we first explore in
\autoref{chap:KullbackLeiblerPureExploration} how the Kullback-Leibler
divergence has been employed in the best arm identification literature
by Garivier and Kaufmann (2016) and Kaufmann et al. (2016) as this will
lead us to our own extension. We shortly describe in
\autoref{sec:VarianceBasedAlgorithms} two variance-based algorithms for
the thresholding bandit problem introduced in Mukherjee et al. (2017)
and Zhang et al. (2017), before introducing the new Simple Likelihood
Ratio algorithm in \autoref{sec:LRforUnivariateExponentialFamily}. We
end in \autoref{chap:Experiments} with experiments to examine the
performance of different algorithms.

@@

To introduce the thresholding bandit problem, consider a game in which
the learner is tasked to find the slot machines within a row of \(K\)
slot machines in a casino that give a mean payoff larger than a fixed
threshold \(\tau\), for example \(\tau = 0\). The learner cannot pull
all slot machines at the same time. Instead, he acquires samples
sequentially from one slot machine at a time to learn about their payoff
structure. The learner has a budget of \(T>K\) slot machine pulls. After
\(t-1\) samples, the learner has observed \(T_i(t-1)\) samples from slot
machine \(i\). The payoffs \(X_{i,1}, ..., X_{i,T_i(t-1)}\) are drawn
from the payoff distribution \(\nu_i\) underlying the slot machine
\(i\). At time \(t\), the learner considers the payoffs he observed so
far in order to choose the next slot machine he would like to pull. Her
decision is lead by the goal to classify the slot machines with
distribution \(\nu_i\) and mean payoff
\(\mu_i = \mathbb{E}_{X \sim \nu_i}[X]\) after \(T\) samples as being
above or below the threshold with error probability as small as
possible.

The thresholding bandit problem can thus be framed in the literature on
sequential sampling strategies. Even though its name is reminiscient of
the multi-armed bandit setting, the thresholding bandit problem is more
akin to best arm identification and top-\(m\) identification problems
due to its focus on exploration: While the classical multi-armed bandit
problems are concerned with cumulative regret which increases
\emph{during} sampling, best arm identification and thresholding bandits
collect loss only once \emph{after} the sampling procedure (compare
Garivier and Kaufmann, 2016; Kaufmann et al., 2016; Kaufmann and
Kalyanakrishnan, 2013). As we will see in
\autoref{chap:KullbackLeiblerPureExploration} there arises an implicit
threshold between the means of the \(m\)-th best arm and the \(m+1\)-th
best arm in the top-\(m\) identification problem (Kaufmann et al., 2016;
Kaufmann and Kalyanakrishnan, 2013). Because of this, the two settings
are very related.

@@

Consider a setting with a set of \(\mathbb{A}=\{1, ..., K\}\) unknown
probability distributions \(\nu_i, i \in \mathbb{A}\). To stick with the
idea of multi-armed bandits, we call the distributions arms, and
observations from the arms rewards (Bubeck and Cesa-Bianchi, 2012). The
learner is interested in learning about the structure of the arms; in
particular, she would like to estimate the means \(\mu_1, ..., \mu_K\)
by sequentially drawing observations \(X_{i,1}, X_{i,2}, ...\) from the
different arms. However, at time \(t\) the learner cannot observe a
reward from every distribution but must select a single arm \(I_t\) from
which she would like to observe the reward \(X_{I_t,t}\). Often,
adaptive sampling strategies makes the decision of which arm to pull by
computing an index \(B_i(t)\) for each arm. If \(T_i(t)\) is the number
of samples observed until time \(t\) for arm \(i\), then is \(B_i(t)\) a
function of the past rewards \(X_{i,1}, ..., X_{i,T_i(t)}\) observed for
arm \(i\), and w.l.o.g. \(I_t = \arg \min_{i = 1,...K} B_i(t)\). The set
of indexes can be called strategy (Kaufmann et al., 2012) which makes it
clear that the strategy is adapted as more observations are collected.
Strategies of this kind are also called index policies.

Which index proves to be useful is determined by the loss function with
which the decisions of the algorithm are evaluated. Many problems are
concerned with finding the arm with the largest mean \(\mu_i^*\) while
collecting loss either cumulatively during (Auer and Cesa-Bianchi, 2012)
or once at the end of the sampling (Kaufmann et al., 2016). The
thresholding bandit problem considers a slightly different loss
function. Consider a fixed threshold value \(\tau \in \mathbb{R}\) and
an epsilon interval \(\tau \pm \epsilon\) around the threshold for
\(\epsilon \geq 0\). As mentioned in the introduction, the learner is
tasked with classifying arms as having a mean \(\mu_i\) larger or
smaller than \(\tau\). As in Locatelli et al. (2016), whenever we say
that ``an arm is over the threshold'', we say that the mean of the arm
is over the threshold. To describe which arms are over the threshold, we
also introduce the following set notation: Let \(\mathcal{S}_{u}\) be
the set of distributions in \(\mathbb{A}\) with mean larger than some
\(u \in \mathbb{R}\):
\(\mathcal{S}_{u} := \{i \in \mathbb{A}, \mu_i \geq u\}\). Consequently,
the complement is given by the arms with mean below \(u\),
\(\mathcal{S}^C_{u} := \{i \in \mathbb{A}, \mu_i < u\}\).

The thresholding problem for the learner is now to use a budget of
overall \(T\) samples (or rounds) to explore the different arms. After
this exploration phase, the learner returns a set of arms that she
believes to be over the threshold. When evaluating the classification of
the learner, arms with mean inside of the epsilon interval
\(\tau \pm \epsilon\) will not be considered. The learner only has to
correctly distinguish the means from the threshold up to the precision
given by \(\epsilon\). Thus, the algorithm is not evaluated against
\(\mathcal{S}_{\tau}\) and \(\mathcal{S}^C_{\tau}\), but needs to
distinguish \(\mathcal{S}_{\tau+\epsilon}\) from
\(\mathcal{S}^C_{\tau-\epsilon}\).

@@

\[
\mathcal{L}(T) = \mathbbm{1}{\big((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \lor (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset)\big)}
\]

In order to perform well, a learner has to identify all arms that are
over the threshold as such, and to not claim arms as being over the
threshold if they actually are below the threshold. Due to the precision
\(\epsilon\), the loss is not influenced by arms which are very close to
the threshold \(\tau\) as measured by \(\epsilon\), that is, arms inside
of the \(\tau \pm \epsilon\) interval. If either
\(\hat{\mathcal{S}}_{\tau}\) contains an arm below
\((\tau - \epsilon)\), or \(\hat{\mathcal{S}}^C_{\tau}\) contains an arm
above \((\tau + \epsilon)\), a loss of \(1\) is accrued. Else, all arms
outside the epsilon interval are classified correctly and the loss is
equal to \(0\). In the case of \(\epsilon = 0\), all arms need to be
classified correctly to not collect any loss.

@@

which corresponds to the probability of making at least one wrong
classification. Both the probability of not identifying an arm that is
actually over the threshold, as well as the probability of accepting an
arm as over the threshold when it is not, are evaluated. The oracle
strategy would evaluate all arms correctly with an error probability of
\(0\) (Locatelli et al., 2016).

At this point, we have introduced the general thresholding bandit
problem setting which we will use throughout the thesis. The setting can
be extended by different assumptions to make certain algorithms or
bounds feasible. For that reason, Locatelli et al. (2016) assume that
the distributions \(\nu_i, i \in \mathbb{A}\) are \(R\)-sub-Gaussian.
Under this assumption, the authors are able to prove a lower bound on
the largest probability of error of the best algorithm in the setting we
have just introduced, as well as an upper bound on the performance of
their APT algorithm which we will introduce in the following chapter. As
in their paper, we define \(R\)-sub-Gaussian and assume it in the
description of the their algorithm and bounds:

@@

As noted by Locatelli et al. (2016), this ensures that the mean
\(\mu_i\) of the distributions \(\nu_i\) considered in our problem are
finite. \(R\)-sub-Gaussian distributions offer concentration
inequalities for the concentration of the empirical mean around the true
mean, which makes it possible to deduce the bounds presented by the
authors and repeated below. The family of \(R\)-sub-Gaussian
distributions encompasses Gaussian distributions of variance \(R^2\) for
\(R \in \mathbb{R}\), as well as all bounded distributions, with the
important case of Bernoulli distributions.

@@

Just like the general index policies mentioned in \autoref{sec:Setup},
we see that the APT algorithm adapts its strategy using an index
\(B_i(t+1)\) for each arm that is based entirely on the observations
observed until time \(t\). Given the arm with the smallest index is
pulled at round \(t+1\), we observe that arms that are estimated to be
further away from the threshold \(\tau\) as measured by the absolute
distance to their empirical mean \(\hat{\mu}_i\), \(\hat{\Delta}_i(t)\),
are pulled less often. Intuitively, it is easier to classify arms as
below or above \(\tau\) when their mean is far away from the threshold.
In contrast to the uniform sampling strategy, APT will gather more
evidence for arms which appear to be inherently more difficult to
classify. Likewise, APT tends to less often pull arms which it already
pulled considerably often as measured by \(T_i(t)\). If arm \(i\) has
been pulled more often than arm \(j\), then we should in general be more
confident in its estimated mean and the corresponding distance to the
threshold. If we are confident in \(i\), then it is better to explore
other arms by drawing an observation from arm \(j\). By adapting its
sampling strategy in this way during the sequential sampling process,
the APT algorithm minimizes the probability of error
\(\mathbb{E}[\mathcal{L}(T)]\) after \(T\) samples have been observed.

The previous paragraph describes how arms close to the threshold are
intuitively more difficult to classify. In the index employed by the APT
algorithm, the distance between an arm and the threshold is measured by
the absolute distance \(\hat{\Delta}_i(t)\) between the (estimated) mean
of the arm and the threshold \(\tau\) (and the epsilon interval). When
the APT algorithm realizes that an arm has a mean close to the
threshold, then this arm requires more attention than an arm far away
from the threshold; the confidence in the empirical mean has to be
larger. Or the empirical mean has to be better concentrated around the
true mean. Otherwise it is easier to make a mistake on this arm. To gain
this confidence, the arm requires more samples, and thus a larger share
of the overall \(T\) samples available. With this intuition, it makes
sense to measure the complexity of a thresholding problem: If we knew
upfront how complex a given set of arms is, we would know whether to
expect a small or large probability of error given our budget \(T\).
Also, for example in the best arm identification problem, there exist
algorithms which take the complexity of a problem as input. Based on the
complexity they then adapt their sampling strategy. See for example the
UCB-E algorithm in Audibert et al. (2010) for the best arm
identification problem, or the KL-LUCB-E algorithm in Kaufmann and
Kalyanakrishnan (2013) as extension to the top-\(m\) problem.

While the APT algorithm does not require the complexity to be known
upfront (which would be problematic as it is not known upfront), it is
necessary to define the complexity to deduce the upper bound on its
probability of error. Similar to the distance measure used in the
algorithm's index, we define the gap \(\Delta_i^{\tau,\epsilon}\)
between arm \(i\) and the threshold \(\tau \pm \epsilon\) as

@@

Note that the complexity of the problem increases in the number of arms
\(K\) and decreases in the gap \(\Delta_i^{\tau,\epsilon}\).
Consequently, when we require less precision, that is, we increase
\(\epsilon\), the hardness decreases. Furthermore, we see that each arm
contributes its individual complexity,
\(h_i^{\tau,\epsilon} = \frac{1}{(\Delta_i^{\tau,\epsilon})^2}\)
linearly into the problem. Thus, if the complexity \(H\) is a good
measure of the actual problem complexity, and we knew upfront which arm
has which mean, we could allocate the ``optimal'' share of the budget,
\(T \cdot h_i /H\) to arm \(i\). However, since we do not know neither
\(\mu_i\) nor \(H\) upfront, the best we can do is to adapt our
allocation of samples more and more towards this optimum as we observe
samples.

@@

In this chapter we present the upper bound on the probability of error
that the APT algorithm incurs, as proven in Locatelli et al. (2016). The
upper bound is on the probability of error that the algorithm has after
\(T\) rounds of sampling for a problem with arms that are assumed to be
\(R\)-sub-Gaussian. The bound depends also on the complexity of the
problem, and we show in the proof that given the index of the APT
algorithm as defined in \autoref{sec:TheAPTAlgorithm}, the complexity
\(H\) is an appropriate measure.

@@

and similar for \(\hat{\Delta}_i\). We can now lower bound the LHS of
the indexes as

@@

\begin{equation}
\kappa_C(\nu) = \inf_{A \, \text{PAC}} \limsup_{\delta \to 0} \frac{\mathbb{E}_{\nu}[T_{\delta}]}{\log \frac{1}{\delta}}. \label{eq:KappaC}
\end{equation}

@@

\begin{equation}
\kappa_B(\nu) = \inf_{A \, \text{consistent}} \Big(\limsup_{t \to \infty} - \frac{1}{t} \log p_t(\nu)\Big)^{-1}.
\end{equation}

@@

@@

\subsection{Means in Simulations 4 and
5}\label{means-in-simulations-4-and-5}
